SubsidyExplorer - Step 5: Run Model

### 2020-08-07 scripts/01_data_wrangling.Rmd

This script handles the preliminary data wrangling for the raw datasets underlying the SubsidyExplorer analysis. It outputs tidyed data files to `r data_dir`. Some of these tidied data files are used directly as input data by the SubsidyExplorer toolkit (saved to `r app_data_dir`).

@@

The RAM Legacy Stock Assessment Database is a compolation of stock assessments for commercially exploited species from around the world. The latest version of this database (version 4.491) was downloaded directly from the RAM website on July 25, 2020 and are stored as `r ram_sadb_path`. 
> RAM Legacy Stock Assessment Database. (2020). Version 4.491-assessment only. Released 2020-02-20. https://doi.org/10.5281/zenodo.3676087

Estimates of stock status for comericlaly exploited species not included in the RAM Legacy Stock Assessment Database from Costello et al. (2016). These data were provided to us directly by the authors and are stored as `r costello_upsides_path`. 
> Costello, C., Ovando, D., Clavelle, T., Strauss, C. K., Hilborn, R., Melnychuk, M. C., Branch, T. A., Gaines, S. D., Szuwalski, C. S., Cabral, R. B., Rader, D. N., & Leland, A. (2016). Global fishery prospects under contrasting management regimes. Proceedings of the National Academy of Sciences, 113(18), 5125–5129. https://doi.org/10.1073/pnas.1520420113

@@

- Proposed tier assignments for a cap-based approach to limiting subsidies as included in the proposal made to the WTO by the delegations of Austraila and the USA on May 3, 2019 [TN/RL/GEN/197/Rev.1].

@@

- A manually compiled table of FAO statistical regions coorepsonding to the stocks contained in version 4.491 of the RAM Legacy Stock Assessment Database.

@@

The naming of flag and coastal states varies widely across our data sources and we recognize that this can be a politially sensitive matter. For the purposes of merging multiple data sources, we therefore translate all state names from the raw data sources to ISO-3 character codes. Country names are only used for display purposes, and the use of any particular name is not meant to convey any options regarding sovereignty on behalf of the authors.

>>>>

This script handles the preliminary data wrangling for the raw data sets underlying the SubsidyExplorer analysis. It outputs tidied data files to `r data_dir`. Some of these tidied data files are used directly as input data by the SubsidyExplorer toolkit (saved to `r app_data_dir`).

@@

The RAM Legacy Stock Assessment Database is a compilation of stock assessments for commercially exploited species from around the world. The latest version of this database (version 4.491) was downloaded directly from the RAM website on July 25, 2020 and are stored as `r ram_sadb_path`. 
> RAM Legacy Stock Assessment Database. (2020). Version 4.491-assessment only. Released 2020-02-20. https://doi.org/10.5281/zenodo.3676087

Estimates of stock status for commercially exploited species not included in the RAM Legacy Stock Assessment Database from Costello et al. (2016). These data were provided to us directly by the authors and are stored as `r costello_upsides_path`. 
> Costello, C., Ovando, D., Clavelle, T., Strauss, C. K., Hilborn, R., Melnychuk, M. C., Branch, T. A., Gaines, S. D., Szuwalski, C. S., Cabral, R. B., Rader, D. N., & Leland, A. (2016). Global fishery prospects under contrasting management regimes. Proceedings of the National Academy of Sciences, 113(18), 5125–5129. https://doi.org/10.1073/pnas.1520420113

@@

- Proposed tier assignments for a cap-based approach to limiting subsidies as included in the proposal made to the WTO by the delegations of Australia and the USA on May 3, 2019 [TN/RL/GEN/197/Rev.1].

@@

- A manually compiled table of FAO statistical regions corresponding to the stocks contained in version 4.491 of the RAM Legacy Stock Assessment Database.

@@

The naming of flag and coastal states varies widely across our data sources and we recognize that this can be a politically sensitive matter. For the purposes of merging multiple data sources, we therefore translate all state names from the raw data sources to ISO-3 character codes. Country names are only used for display purposes, and the use of any particular name is not meant to convey any options regarding sovereignty on behalf of the authors.

### 2020-08-07 scripts/02_vessel_list.Rmd

# Do you wnat to make figures? 
make_figures <- FALSE

@@

Quick summary of our global vessel list by gear type:

```{r}
if(make_figures){
# Summary by gear type
vessels_by_gear <- vessel_list_out %>%
  group_by(vessel_class) %>%
  summarize(count = n_distinct(ssvid),
            flag_states = n_distinct(flag_iso3),
            fao_regions = n_distinct(fao_region),
            length_avg = mean(length_m, na.rm = T),
            tonnage_avg = mean(tonnage_gt, na.rm = T),
            engine_power_avg = mean(engine_power_kw, na.rm = T),
            fishing_hours = sum(fishing_hours_eez_fao_ter, na.rm = T),
            fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T))

>>>>

# Do you wnat to make figures? 
make_plots <- FALSE

# Few more packages if you're making figures
if(make_plots){
  library(forcats)
}

@@

```{r}
if(make_plots){
# Summary by gear type
vessels_by_gear <- vessel_list_out %>%
  group_by(vessel_class) %>%
  summarize(count = n_distinct(ssvid),
            flag_states = n_distinct(flag_iso3),
            fao_regions = n_distinct(fao_region),
            length_avg = mean(length_m, na.rm = T),
            tonnage_avg = mean(tonnage_gt, na.rm = T),
            engine_power_avg = mean(engine_power_kw, na.rm = T),
            fishing_hours = sum(fishing_hours_eez_fao_ter, na.rm = T),
            fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T))

### 2020-08-07 scripts/03_management.Rmd

# Few more packages if you're making figures
if(make_plots){
  library(ggridges)
  library(ggrepel)
  library(scales)
}
```

@@

>>>>

# Few more packages and dataif you're making figures
if(make_plots){

  library(ggridges)
  library(ggrepel)
  library(scales)
  library(sf)

  # 1) World map ---
  world <- read_sf(here::here("app", "data", "shapefiles", "ne_50m_admin_SubsidyExplorer"), layer = "land_50m")

  # 2) EEZs/FAO regions ---
  eez_fao <- read_sf(dsn = here::here("app", "data", "shapefiles", "eez-v10-fao-combined-simple"), layer="eez_v10_fao_combined_simple") %>%
    mutate(eez_hs_code = ifelse(!is.na(zone), paste0("HS-",zone), as.character(mrgid)))

@@

  # Summarize data
    fmi_map_dat <- eez_fao %>%
      left_join(eez_management_indices %>% mutate(eez_hs_code = as.character(eez_id)), by = c("eez_hs_code")) %>%
      mutate(fmi_best = ifelse(is.na(fmi_best), 0.21, fmi_best))

  fmi_map <- ggplot()+
    geom_sf(data = world, fill = "black", color = "grey", size = 0.25)+
    geom_sf(data = fmi_map_dat, aes(fill = fmi_best), color = "grey", size = 0.25)+
    theme_bw()+
    scale_fill_distiller(palette = "YlGn", 
                         direction = 1,
                         limits = c(0.2, 1))+
    labs(fill = "FMI Score")

  ggsave(paste0(results_dir, "fmi_score_map.png"), width = 7.5, units = "in")
}
```

### 2020-08-07 scripts/04_model_parameterization.Rmd

# Add MSY to parameter table
global_model_parameters <- global_model_parameters %>%
  bind_rows(tibble(parameter = "MSY", value = global_msy, source = "Costello et al. 2016"))

@@

# Add K to parameter table
global_model_parameters <- global_model_parameters %>%
  bind_rows(tibble(parameter = "K", value = global_k, source = "Costello et al. 2016; World Bank 2017"))
```

@@

# Add g to parameter table
global_model_parameters <- global_model_parameters %>%
  bind_rows(tibble(parameter = "r", value = global_g, source = "Costello et al. 2016"))
```

@@

# Add base year biomass to parameter table
global_model_parameters <- global_model_parameters %>%
  bind_rows(tibble(parameter = "B0", value = global_b0, source = "FAO 2019; World Bank 2017"))
```

@@

# Add MSY to the regional paramter table
regional_model_parameters <- regional_model_parameters %>%
  bind_rows(c("parameter" = "MSY", "source" = "Costello et al. 2016", regional_msy))
```

@@

# Add MSY to the regional paramter table
regional_model_parameters <- regional_model_parameters %>%
  bind_rows(c("parameter" = "K", "source" = "Costello et al. 2016; World Bank 2017", regional_k))
```

>>>>

# Add MSY to parameter table
global_model_parameters <- global_model_parameters %>%
  bind_rows(tibble(parameter = "msy", value = global_msy, source = "Costello et al. 2016"))

@@

# Add K to parameter table
global_model_parameters <- global_model_parameters %>%
  bind_rows(tibble(parameter = "k", value = global_k, source = "Costello et al. 2016; World Bank 2017"))
```

@@

# Add g to parameter table
global_model_parameters <- global_model_parameters %>%
  bind_rows(tibble(parameter = "r", value = global_r, source = "Costello et al. 2016"))
```

@@

# Add base year biomass to parameter table
global_model_parameters <- global_model_parameters %>%
  bind_rows(tibble(parameter = "b0", value = global_b0, source = "FAO 2019; World Bank 2017"))
```

@@

# Add MSY to the regional paramter table
regional_model_parameters <- regional_model_parameters %>%
  bind_rows(c("parameter" = "msy", "source" = "Costello et al. 2016", regional_msy))
```

@@

# Add MSY to the regional paramter table
regional_model_parameters <- regional_model_parameters %>%
  bind_rows(c("parameter" = "k", "source" = "Costello et al. 2016; World Bank 2017", regional_k))
```

### 2020-08-07 scripts/06_run_model.Rmd

```{r}
# Source model script

@@

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

```{r}
# Source model script
source(here::here("app", "scripts", "BioEconModel.R"))
```

```{r}
# Load vessel list
pro_rate_subsidies <- F

vessel_dat <- read.csv(here::here("app", "data", "vessel_list_2018_final.csv"), stringsAsFactors = F)

if(pro_rate_subsidies == T){

  vessel_dat <- vessel_dat %>%
    mutate(B1_subs = B1_subs * 0.54, # boat construction/renovation - matched to payments based on vessels
           B2_subs = B2_subs * 1, # fishery development projects/support services - matched to payments based on variable use
           B3_subs = B3_subs * 0.87, # port construction and renovation - matched to payments based on vessels
           B4_subs = B4_subs * 0.87, # price/marketing support, processing infrastructure - matched to payments based on output
           B5_subs = B5_subs * 0.76, # non-fuel tax exemptions - matched to payments based on fishers income
           B6_subs = B6_subs * 0.56, # foreign access agreements - matched to payments based on fishers own capital
           B7_subs = B7_subs * 0.84, # fuel - matched to payments based on fuel use
           bad_subs = (B1_subs + B2_subs + B3_subs + B4_subs + B5_subs + B6_subs + B7_subs))

}

vessel_dat <- vessel_dat %>%
  mutate(eez_hs_code = case_when(eez_id == 0 ~ paste0("HS-", fao_region),
                                 TRUE ~ as.character(eez_id)))
```

```{r}
# Load biological parameters for the model
bio_dat_global <- read.csv(here::here("app", "data", "model_parameters_global.csv"))
bio_dat_regional <- read.csv(here::here("app", "data", "model_parameters_regional.csv"))

# Regional parameter list
bio_dat_regional_list <- bio_dat_regional %>%
  gather(region, value, -c(1:2)) %>%
  group_by(region) %>%
  group_split()
```

```{r}
# Get WTO countries territories
```

```{r}
# Threshold to be considered managed
managed_cutoff <- 0.66
```

## Create global fleet

```{r pressure, echo=FALSE}
# Assign fleets to vessels
global_fleet_vessels <- vessel_dat %>%
  mutate(is_WTO = ifelse(flag_iso3 %in% c(cap_tier_dat$iso3, eu_countries, eu_territories, us_territories, norwegian_territories), T, F)) %>%
  mutate(fleet = case_when(is_WTO & fmi_best >= managed_cutoff & bad_subs > 0 ~ "affected_managed",
                           is_WTO & fmi_best < managed_cutoff & bad_subs > 0 ~ "affected_oa",
                           (!is_WTO & fmi_best >= managed_cutoff) ~ "unaffected_managed",
                           (!is_WTO & fmi_best < managed_cutoff) ~ "unaffected_oa",
                           TRUE ~ "unaffected_oa"))

# Create fleet (summary)
global_fleet_summary <- global_fleet_vessels %>%
  group_by(region, fleet) %>%
  summarize(catch = sum(catch, na.rm = T),
            bad_subs = sum(bad_subs, na.rm = T),
            fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T),
            removed_subs = sum(bad_subs, na.rm = T))
```

## Run Model (Remove all bad subsidies)

```{r}

@@
